Paper draft: Predicting Erectile Function in Patients Undergoing Stereotactic Body Radiation Therapy

### 2017-01-22 paper_draft.Rmd
sss

In this study, data collected from SBRT patients is used to fit a logistic regression model exploring the likelihood of losing erectile function following treatment with SBRT. The model shows that variables such as age, score on a health survey, and prostate-specific antigen levels can be used to predict the probability of erectile function two years post-treatment with reasonably high accuracy.

## Methods
Our analysis consists of two parts. In the first part, we carry out a series of exploratory data analysis in order to understand the data in general so that we can choose an appropriate statistical model to build, and in the second part we build a logistic regression model to predict the probability that one will have erectile function at two years after SBRT.

>>>>

In this study, data collected from SBRT patients is used to fit a logistic regression model exploring the likelihood of losing erectile function following treatment with SBRT. The data included baseline variables such as: age; Gleason score, the grade of the patient's cancer; prostate-specific antigen (PSA), a continuous measurement from a blood test associated with aggressiveness of one's cancer; T-Stage Group, categorizing the size and spread of the tumor; androgen deprivation therapy (ADT), a variable indicating whether or not the patient was chemically castrated; body-mass index (BMI), a measure of height-to-weight ratio; and erectile function. A more detailed look at our variables can be found in Table XX.

Our model shows that age, score on a health survey, and prostate-specific antigen levels can be used to predict the probability of erectile function two years post-treatment with reasonably high accuracy.

### Variables
- Age
- Gleason Score
- PSA
- T-Stage Group
- ADT
- BMI
- Erectile Function at Baseline
- Erectile Function at 2 years

## Methods
Clinical and biomarker data were collected from 325 patients with prostate cancer that experienced SBRT and were followed for 2 years or longer between 2008 and 2013. All the patients in the data were treated at a single institution.

Our analysis consists of two parts. In the first part, we carry out a series of exploratory data analysis in order to understand the data in general so that we can choose an appropriate statistical model to build, and in the second part we build a logistic regression model to predict the probability that one will have erectile function at two years after SBRT.
